Estimating duration in the presence of misclassification

### 2024-07-29 transmission.tex
Rob p135 comment
Rob p147 comment

$p_0$ increases at the same rate as individuals flow into $e_1$.
These individuals then transition into a set of compartments, $p_1, \dots, p_l$, each with their own transition rate.
I will choose $l$ and the transition rates such that combined length of stay (\ie time from entry in $p_1$ until exit from $p_l$) approximates the duration of detectability distribution estimated in \cref{E-imperf-test}.
This idea extends the technique of having multiple exposed or latent compartments (introduced in \cref{E-SEIR:sec:non-exponential}).
While the use of exponential or Erlang (gamma distributions with integer first parameter) is common in the observation model of compartmental models~\autocite[e.g.][]{overtonEpiBeds}, the use of more flexible phase-type distributions, as here, has rarely, if ever, been used in practice~\autocite{hurtadoGLCT}.
This broader class of distributions allows the model to capture the tail of the distribution, which is important when incidence suddenly decreases.

@@

The $\beta_w$ parameters absorb all the time-varying changes in transmission not captured by Google mobility and school attendance data.
They trend downwards up until early December, then they start increasing (see \cref{SEIR:fig:beta-walk}).
Correlation is clear across the regions even though each region is estimated independently, suggesting underlying biological or epidemiological changes across regions.

>>>>

$p_0$ increases at the same rate as individuals flow into $e_1$.
These individuals then transition into a set of compartments, $p_1, \dots, p_l$, each with their own transition rate.
Individuals in compartments $p_1, \dots, p_l$ are detectable; exiting compartment $p_l$ corresponds to the end of the detectable period.
I will choose $l$ and the transition rates such that combined length of stay (\ie time from entry in $p_1$ until exit from $p_l$) approximates the duration of detectability distribution estimated in \cref{E-imperf-test}.
This idea extends the technique of having multiple exposed or latent compartments (introduced in \cref{E-SEIR:sec:non-exponential}).
While the use of exponential or Erlang (gamma distributions with integer first parameter) is common in the observation model of compartmental models~\autocite[e.g.][]{overtonEpiBeds}, the use of more flexible phase-type distributions, as here, has rarely, if ever, been used in practice~\autocite{hurtadoGLCT}.
This broader class of distributions allows the model to capture the tail of the distribution, which is important when incidence suddenly decreases.

@@

The $\beta_w$ parameters absorb all the time-varying changes in transmission not captured by Google mobility and school attendance data.
They trend downward and are then flat until they begin rising around the start of December (see \cref{SEIR:fig:beta-walk}).
Correlation is clear across the regions even though each region is estimated independently, suggesting underlying biological or epidemiological changes across regions.
